Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-15 ICML-submission/from-weak-separability-to-strong-separability.tex
some intuition in Sect 5.1

\subsection{Proof of Theorem~\ref{theorem:margin-transformation}}
\label{sec:margin-trans}
The idea behind construction and analysis of the mapping $\phi$ is polynomial
approximation. According to the well known Stone-Weierstrass theorem (see
e.g.~\citet[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
multivariate polynomials uniformly approximate any continuous function.
Intuitively speaking, we use a multivariate polynomial to approximate, on the
unit ball of $\R^d$, the indicator function corresponding to the intersection of
$m=K-1$ halfspaces. Within margin $\gamma$ along the decision boundary, we allow
the polynomial to attain arbitrary value. The polynomial separates examples in
one class from examples in the other classes. To be able to quantify $\gamma'$
we need to quantify certain parameters of the approximating polynomial. We
construct two different polynomials with different parameters. The parameters
are quantified in
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
stated below.

>>>>

\subsection{Proof of Theorem~\ref{theorem:margin-transformation}}
\label{sec:margin-trans}
\paragraph{Overview.} The idea behind construction and analysis of the mapping $\phi$ is polynomial
approximation. Specifically, we give $k$ polynomials $p_1$, $\ldots$, $p_k$,
such that:
\begin{equation}
  \forall t \in \cbr{1,2,\ldots,T}, p_{y_t}(x_t) \geq \frac{\gamma'}2,
  \label{eqn:poly-pos}
\end{equation}
\begin{equation}
  \forall t \in \cbr{1,2,\ldots,T}, \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t}, p_i(x_t) \leq -\frac{\gamma'}2.
  \label{eqn:poly-neg}
\end{equation}
As each polynomial $p_i$ can be written as
$\ip{c_i}{\phi(x)}$ for some $c_i \in \ell_2$, it immediately shows that
the set of examples $(\phi(x_1),y_1), \ldots, (\phi(x_T),y_T)$ is strongly linear separable.

To construct $p_1, \ldots, p_k$ that satisfy Equations~\eqref{eqn:poly-pos}
and~\eqref{eqn:poly-neg}, we consider constructing each $p_i$ separately.
Specifically, $p_i$ needs to satisfy that:
\begin{equation}
  \forall t \in \cbr{1,2,\ldots,T}, y_t = i \Rightarrow p_i(y_t) \geq \frac{\gamma'}2,
  \label{eqn:poly-pos-i}
\end{equation}
\begin{equation}
  \forall t \in \cbr{1,2,\ldots,T}, y_t \neq i \Rightarrow p_i(y_t) \leq -\frac{\gamma'}2.
  \label{eqn:poly-neg-i}
\end{equation}

Under the weak linear separability assumption, we note that all examples from class $i$
lie in
$R_i^+ := \cap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \geq \gamma}$, and all examples from other classes lie in
$R_i^- := \cup_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \leq  -\gamma}$.
Therefore, to satisfy Equations~\eqref{eqn:poly-pos-i} and~\eqref{eqn:poly-neg-i},
it suffices to construct $p_i$ such that:
\begin{align*}
  x \in R_i^+ & \Rightarrow p_i(x) \geq \frac {\gamma'} 2\\
  x \in R_i^- & \Rightarrow p_i(x) \leq - \frac {\gamma'} 2
\end{align*}

According to the well known Stone-Weierstrass theorem (see
e.g.~\citet[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
multivariate polynomials uniformly approximate any continuous function.
Intuitively speaking, we use a multivariate polynomial to approximate, on the
unit ball of $\R^d$, the indicator function corresponding to the intersection of
$m=K-1$ halfspaces. Within margin $\gamma$ along the decision boundary, we allow
the polynomial to attain arbitrary value. The polynomial separates examples in
one class from examples in the other classes. To be able to quantify $\gamma'$
we need to quantify certain parameters of the approximating polynomial. We
construct two different polynomials with different parameters. The parameters
are quantified in
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
stated below.
